---
title: "Assignment 3"
author: "Georgia Galanopoulos"
date: "February 19, 2017"
output: html_document
---

##**Exercise 3**
```{r}
library(stringr)

raw.data = "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

```


**3 part 1**
*Rearrange vector to look like first_name last_name *
```{r}
name = unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
name_order = gsub(" [A-Z]{1}\\. " , " " , name)
first_last = gsub("(\\w+),\\s(\\w+)", "\\2 \\1", name_order)
first_last
```


**3 part 2**
*Create logical vector indicating title (Rev or Dr) *
```{r}
title = unlist(str_detect(name,"[[:alpha:]]{2,}[.]"))
data.frame(first_last,title)
```


**3 part 3** *Create logical vector indicating if second name? *
```{r}
name_two = str_detect(name," [A-z]{1}\\. ")
data.frame(name, first_last, title, name_two)
```

##**Exercise 4**

*Describe the types of strings. Below I have constructed examples for the given expressions involving passwords and determining if the criteria from each string allow each password to hold.*


**4 part 1**
*[0-9]+\\$*

String containing a pattern of one or more numbers with a dollar sign
```{r}
passwords = c("3Ccwk4DRd", "KXX7$GUxm.txt", "fHk$FgWEF", "3w8zm4Xs", "D98$EAcHw")
hold = str_detect(passwords, "[0-9]+\\$")
data.frame(passwords, hold)
```


**4 part 2**
*\\b[a-z]{1,4}\\b*

String containing up to four lower case letters, so long as those lower case letters are word edges
```{r}
passwords = c("3C.cwk.4DRd", "3w8zm4Xs", "V386$h68A", "wrCyQQcw")
hold = str_detect(passwords, "\\b[a-z]{1,4}\\b")
data.frame(passwords, hold)
```


**4 part 3**
.*?\\txt$ 

String pattern ending in ".txt"
```{r}
hold = str_detect(passwords, ".*?\\.txt$")
data.frame(passwords, hold)
```


**4 part 4**
*\\d{2}/\\d{2}/\\d{4}*

String containing pattern of two digits followed by a front slash, two more digits, another front slash and finally four digits.
```{r}
passwords = c("02\02\0202", "45689587", "56/85/1538", "87-98-4585")
hold = str_detect(passwords, "\\d{2}/\\d{2}/\\d{4}")
data.frame(passwords, hold)
```


**4 part 5**
*<(.+?)>.+?</\\1>*

String pattern containing tags.

```{r}
passwords = c("<nope>yep</no>", "KXX7$GUxm.txt", "<tag>hi</tag>", "fHk$FgWEF")
hold = str_detect(passwords, "<(.+?)>.+?</\\1>")
data.frame(passwords, hold)
```



##**Exercise 9**

*Crack the code.*
```{r}
code = "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

cracked = unlist(str_extract_all(code, "[[A-Z].!]"))
paste(cracked, collapse = "")
```


*Answer to the code.*
```{r}
newcode = "clcopTow1zmstc0d87wnkig7HvdicpIuggvhryn92Sjuwczi8hqrfp.xs5Ij5dwpn0Sanwo.wisdij7Tj8kpf03HE5.dr3coc0bt7yczjatCaootj55t3Oj3ne6c4OfekLr1w1EwwojigSd6vrfTrbz2.2bkEnbhzgv4X9i05zTcropRwAgnb.CqoR65fEa1otfb7wDm24k6t3sI9zqe5fy89n6Td5t9kc4f!905gmc4gxo5nhkgr"
RosettaStone = unlist(str_extract_all(newcode, "[[:upper:].!]"))
answer = paste(RosettaStone, collapse = "")
```